\documentclass[12pt]{article}
\begin{document}

\title{\textbf{Proof of Concept Demonstration Plan}}
\author{Joshua Voskamp, Mohammed Naveed, Stephan Arulthasan}
\date{\today}
\maketitle

\noindent{\textbf{Will a part of the implementation be difficult?}}

Implementing the modelling of where the tiles are supposed to appear when the user hits the direction keys will be the most difficult part of the project. Furthermore, implementing the graphical user interface will also be difficult, specifically the sizing of the tiles and window size for each user. Currently, this is an issue, as the size of the UI does not scale properly with respect to the user's screen resolution. 

\noindent{\textbf{Will testing be difficult?}}

There is no real way to test the entire application, as it is a game that can only be won once you reach a certain tile. There is no set algorithm that guarantees a winning play, since the position of where the tiles appear are randomized every single time. The only way to go about testing this application is to use unit testing, individually testing each class for correctness and checking if different states are valid, determining the overall correctness of the application based on the output.

\noindent{\textbf{Will portability be a concern?}}

Portability should not be a concern as the application is implemented in java which is available cross-platform. The application can be run on any platform carrying the Java runtime environment. 

\noindent{\textbf{What is the feasibility of this project?}}

Overall our team is comfortable with the implementation of this project because we are very comfortable with the programming language and the application logic. 

\end{document}
